Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-05-13 ms.tex
final initial casey comments

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion using probability based and machine learning methods. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ new Visible Integral-Field Replicable Unit Spectrographs (VIRUS), over 420 \degsq\ on the sky with a 1/4.5 fill factor. The instrument covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$. \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with Targeted observations.}
\end{abstract}

@@

\editorial{There are quite a few words copied from Casey's SHELA paper.}
HETDEX will perform a blind survey which will measure the redshifts of $8 \times \sim 10^5$ Ly$\alpha$ emitting galaxies (LAEs) between $1.9 < z < 3.5$ using a collection of 78 wide-field IFUs spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}. The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX. The result will be a significant constraint on the evolution of dark energy that is competitive with (and independent of) values based on surveys of the Ly$\alpha$ forest.

@@

\subsection{Mock Observations}\label{sec: observations}
This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly decreased from the expected filling factor of 1/4.5.

In this work we consider two separate observing strategies, Targeted and Survey-like. The Targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed. The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of Targeted observations with ``perfect'' knowledge. Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected. This provides an important best-case scenario, and differs from the true cluster properties because the cluster properties are still calculated. These observations provide three levels of quality with ``Perfect knowledge'' being the highest and Survey being the lowest.

\section{Recovery of Parameters}\label{sec:recovery}
In the following subsections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Boada2016a}.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $p(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
C_{BI} = M + \frac{\sum_{|u_i| < 1} (x_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $x_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(x_i - M)}{c\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $c$ is the a tuning constant. We choose $c=6$ (the suggested value) which balances computational speed and location accuracy.

@@

\subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
We calculate the LOSV to each galaxy, where
\begin{equation}
	\mathrm{LOSV} = c\frac{z - z_c}{1+z_c}
\end{equation}
and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous section.

We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
\end{equation}
where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms. We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data \citeeg{Boada2016a}.

@@

A growing body of work suggests that there is a significant difference in the observed LOSVD depending on the velocity tracers used. Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}. We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies, which rely on galaxies as tracers.

@@

\subsubsection{Probability Based}\label{sec:probability method}
For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features. In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the ``training'' set).

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma
\end{equation}
The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' cluster mass, $M_{pred}$.
\begin{equation}\label{eq: expected mass}
	M_{pred}= \int M_{200c}\ P(M_{200c})\ dM_{200c}
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the second moment of the probability density through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M_{200c} - M_{pred})^2\ P(M_{200c})\ dM_{200c}
\end{equation}
or by drawing many samples from $P(M_{200c})$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.

@@

We compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift (and therefore LOSV) of each galaxy in the cluster is known perfectly).

@@

As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number of clusters member galaxies expected to be recovered. Knowing these limits will provide important information for potential future follow up or Targeted observations. Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as a function of both redshift and cluster mass. We require a detection of ($N_{obs} >=5$) galaxies for a cluster to be “detected” and included in this figure. As expected, the Targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the Survey observing strategy across all redshifts and cluster masses. With Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses.

For the clusters recovered as a function of redshift (y-direction of Figure~\ref{fig: recovery}), there are two effects at work. The decrease in recovery fraction with increasing redshift is a magnitude effect. Increasing redshift results in a lower galaxy recovery fraction. Because HETDEX is limited in apparent magnitude, we expect to recovery fewer galaxies at higher redshift. We confirm this by limiting the cluster galaxy detection by absolute magnitude, by observing all galaxies with $M_g < -11$. This increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold. The second key feature is the strong decline in clusters recovered from Survey observations. This is due to gaps in the VIRUS IFU. The median recovery fraction in Survey observations is almost exactly 4.5 times less than the Targeted median recovery fraction. As the total filling factor of the Survey increases the two lines will converge.

The recovery rate as a function of cluster mass, x-direction of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), we observe the majority of the galaxies. This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes, as above. Because there are few high mass ($M>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass. If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across all masses. Again perfect observations would detect all members, at all masses, so in this way, Figure~\ref{fig: recovery} is really just a statement about the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey.

@@

In this section we discuss the how accurately we recover the true cluster mass from a set of observations. We report on three methods, the power law based approach (Eq. \ref{eq:power law}), the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}). For each method we consider observations with Perfect knowledge, Targeted observations and Survey observations. The cluster masses presented here are recovered using the best possible conditions, where we have Perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.

Because it represents the best possible scenario, the Perfect knowledge observations should serve as baseline to compare the power law based, probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
\begin{equation}
\mathrm{\mu_{bias}}(y,y_{pred}) = \frac{1}{N} \sum_{i=1}^N (y_{pred,i} - y_i).
\end{equation}
where $y$ are the true values and $y_{pred}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
\begin{equation}
	\sigma_{bias}(y,y_{pred}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (y_{pred,i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
\end{equation}
with $N$ clusters in a given bin. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.

@@

Qualitatively, the top panels of Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison} show that both the probability based and ML based methods out perform (closer to the black 1:1 relation) the power law method when taking advantage of other cluster observables ($z$, $N_{gal}$, etc.). Generally, we find that the single parameter probability and ML methods perform significantly poorer than the power law method, especially at low cluster masses. When combined with the cluster redshift, the predicted cluster masses are improved, even though it is unclear exactly why the additional information should effect the predicted cluster mass. The final addition of the number of observed galaxies, $N_{gal}$ acts as a type of richness estimate, and significantly improves both the bias and the amount of scatter in the predicted masses.

>>>>

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observations of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion using probability based and machine learning methods. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ new Visible Integral-Field Replicable Unit Spectrographs (VIRUS), over 420 \degsq\ on the sky with a 1/4.5 fill factor. VIRUS covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. We find that with HETDEX we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted followup observations. This level of cluster mass recovery enables us to place $<20$\% constraints on $\sigma_8$, and leverage the unique properties of the observations to provide important calibrations for the optical richness-cluster mass relation.
\end{abstract}
% Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
% \end{abstract}

@@

\editorial{There are quite a few words copied from Casey's SHELA paper.}
HETDEX will perform a blind survey which will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFUs spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}. The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX. The result will be a significant constraint on the evolution of dark energy that is competitive with (and independent of) values based on surveys of the Ly$\alpha$ forest.

@@

\subsection{Mock Observations}\label{sec: observations}
This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a turquoise, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly decreased from the expected filling factor of 1/4.5.

In this work we consider two separate observing strategies, Targeted and Survey. The Targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed. The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of Targeted observations with ``perfect'' knowledge. Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected. This provides an important best-case scenario, and differs from the true cluster properties because the cluster properties are still calculated. These observations provide three levels of quality with ``Perfect knowledge'' being the highest and Survey being the lowest.

\section{Recovery of Parameters}\label{sec:recovery}
In the following subsections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Kirk2015, Boada2016a}.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $p(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
C_{BI} = M + \frac{\sum_{|u_i| < 1} (x_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $x_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(x_i - M)}{C\,\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.

@@

\subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
We calculate the LOSV to each galaxy, where
\begin{equation}
	\mathrm{LOSV} = c\frac{z - z_c}{1+z_c}
\end{equation}
and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous subsection.

We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
\end{equation}
where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms. We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the second momment of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_{1D}$. In simple tests where the values of both $\sigma_{1D}$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data \citeeg{Boada2016a}.

@@

A growing body of work suggests that there is a significant difference in the observed LOSVD depending on the velocity tracers used. Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}. We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} to facilitate comparisons with other observational studies, which rely on galaxies as tracers.

@@

\subsubsection{Probability Based}\label{sec:probability method}
For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features. In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the training set).

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$, the LOSVD, through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma
\end{equation}
The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' cluster mass, $M_{pred}$.
\begin{equation}\label{eq: expected mass}
	M_{pred}= \int M_{200c}\ P(M_{200c})\ dM_{200c}
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the second moment of the probability density through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M_{200c} - M_{pred})^2\ P(M_{200c})\ dM_{200c}
\end{equation}
or by drawing many samples from $P(M_{200c})$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.

@@

We compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift (and therefore LOSV) of each galaxy, regardless of observational limits, in the cluster is known perfectly.

@@

As discussed in Section \ref{sec: observations}, the observational constraints place limits on the total number of clusters member galaxies expected to be recovered. Knowing these limits will provide important information for potential future follow up or Targeted observations. Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as a function of both redshift and cluster mass. We require a detection of $N_{obs} >=5$ galaxies for a cluster to be ``detected'' and included in this figure. As expected, the Targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the Survey observing strategy across all redshifts and cluster masses. With Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses where clusters exist.

For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the pattern of decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits imposed. Because HETDEX is limited in apparent magnitude, we expect to recovery fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold. We confirm this by converting all observed galaxies apparent magnitudes into absolute magnitudes and then limiting our survey to galaxies with $M_g < -11$ Mag. This increases the recovery fraction to $>70\%$ at all redshifts.

For the recovery fraction as a function of true cluster mass (x-direction), we find a general decrease in the recovery fraction of member galaxies with increasing cluster mass. We also find that, in general, cluster mass increasing with increasing redshift. This causes our recovery fraction as a function of cluster mass to suffer from the same magnitude effects as discussed previously. Because there are few high mass ($M_{200c}>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass. If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, across all masses, increases substantially, and we find a much more consistent detection fraction across all masses.

For the Survey observations, the right panel of Figure~\ref{fig: recovery}, all of the same effects are at work. In addition we find that the fill factor, due to the gaps between the VIRUS IFUs, further reduces the number of cluster members detected. The median recovery fraction in Survey observations is almost exactly 4.5 times less than the Targeted median recovery fraction. As the total filling factor of the Survey observations increases the two lines will converge.

Figure~\ref{fig: recovery} is really just a statement about the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey. For Perfect observations, we would detect all members across all cluster masses and redshifts. Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by followup targeted observations. But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from followup observations regardless of the redshift. So followup observations should be tailored to the specific science goal.

@@

In this section we discuss the how accurately we recover the true cluster mass from a set of observations. We report on three methods, the power law based approach (Eq. \ref{eq:power law}), the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}). For each method we consider observations with Perfect knowledge, Targeted observations and Survey observations. The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.

Because it represents the best possible scenario, the Perfect knowledge observations should serve as baseline to compare the power law based, probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
\begin{equation}\label{eqn: bias}
\mathrm{\mu_{bias}}(y,y_{pred}) = \frac{1}{N} \sum_{i=1}^N (y_{pred,i} - y_i).
\end{equation}
where $y$ are the true values and $y_{pred}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
\begin{equation}\label{eqn: scatter}
	\sigma_{bias}(y,y_{pred}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (y_{pred,i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
\end{equation}
with $N$ clusters in a given bin. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.

@@

Qualitatively, the top panels of Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison} show that both the probability based and ML based methods out perform (closer to the black 1:1 relation) the power law method when taking advantage of other cluster observables ($z$, $N_{gal}$, etc.). Generally, we find that the single parameter probability and ML methods perform significantly poorer than the power law method, especially at low cluster masses. When combined with the cluster redshift, the predicted cluster masses are improved, because the range of cluster masses decrease with increasing redshift (see Figure~\ref{fig: recovery}). The final addition of the number of observed galaxies, $N_{gal}$ acts as a type of richness estimate, and significantly improves both the bias and the amount of scatter in the predicted masses.

\begin{table*}
\centering
\caption{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccc} 
		&& \multic{6}{Bins -- Log $M_{pred}$} \\
		\cline{3-8} 
		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline
		&& \multic{6}{Perfect Observations} \\
		\hline 
		\rottext{4}{Prob Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
		&$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
		&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & $-6.62\pm{3.742}$ \\
		\hline
		\rottext{5}{ML Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
		&$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
		&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
		&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
		\hline
